Power and Pitfalls of Generic Smart Contracts

### 2022-02-22 cluster_computing/020_shared_entities_with_generics.tex
figures

A \emph{shared entity} is concept that often arises in blockchain
applications. Namely, a shared entity is something divided into \emph{shares}. Participants,
that hold shares, are called \emph{shareholders} and can dynamically
sell and buy shares. An example of a shared entity is a corporation,
where shares represent units of possess of the company. Another example is
a voting community, where shares represent the voting power of each given voter.
A further example is the set of the validator nodes of a proof of stake blockchain,
where shares represent their voting power and remuneration percentage.

@@

    public Offer(S seller, BigInteger sharesOnSale, BigInteger cost, long duration) {
      this.seller = seller;
      this.sharesOnSale = sharesOnSale;
      this.cost = cost;
      this.expiration = now() + duration;
    }

@@

The \<SharedEntityView> interface at the top of the hierarchy in Fig.~\ref{fig:hierarchy-entities}
defines the read-only operations on a shared entity. This view is \emph{static}, in the sense that it
does not specify the operations for transfers of shares. Therefore, its only type parameter is \<S>:
any contract can play the role of the type for the shareholders of the entity.
Method \<getShares> yields a snapshot of the
current shares of the entity (who owns how much). Method \<getShareholders> yields the shareholders.
It is not \<@View>, since it creates a new stream, which is a side-effect.
Method \<isShareholder> checks if an object is a shareholder. Method \<sharesOf> yields
the number of shares of a shareholder. As typical in Takamaka, a \<snapshot> method allows one
to create a frozen read-only copy of an entity (in constant time), useful when an enity must be queried from
a client without the risk of race conditions if another client is modifying the same entity concurrently.

\begin{figure}[t]
  \begin{center}
    \begin{lstlisting}[language=Takamaka]
public class SimpleSharedEntity
    <S extends PayableContract,O extends Offer<S>>
    extends PayableContract implements SharedEntity<S,O> {

@@

>>>>

A \emph{shared entity} is a concept that often arises in blockchain
applications. Namely, a shared entity is something divided into \emph{shares}. Participants,
that hold shares, are called \emph{shareholders} and can dynamically
sell and buy shares. An example of a shared entity is a corporation,
where shares represent units of possess of the company. Another example is
a voting community, where shares represent the voting power of each given voter.
A further example is the set of the validator nodes of a proof of stake blockchain,
where shares represent their voting power and remuneration percentage.

@@

    public Offer(S seller, BigInteger sharesOnSale, 
                 BigInteger cost,long duration) {
      this.seller = seller;
      this.sharesOnSale = sharesOnSale;
      this.cost = cost;
      this.expiration = now() + duration;
    }

@@

\begin{figure}[tp]
  \begin{center}
    \begin{lstlisting}[language=Takamaka]
public class SimpleSharedEntity
    <S extends PayableContract,O extends Offer<S>>
    extends PayableContract implements SharedEntity<S,O> {

@@

The \<SharedEntityView> interface at the top of the hierarchy in Fig.~\ref{fig:hierarchy-entities}
defines the read-only operations on a shared entity. This view is \emph{static}, in the sense that it
does not specify the operations for transfers of shares. Therefore, its only type parameter is \<S>:
any contract can play the role of the type for the shareholders of the entity.
Method \<getShares> yields a snapshot of the
current shares of the entity (who owns how much). Method \<getShareholders> yields the shareholders.
It is not \<@View>, since it creates a new stream, which is a side-effect.
Method \<isShareholder> checks if an object is a shareholder. Method \<sharesOf> yields
the number of shares of a shareholder. As typical in Takamaka, a \<snapshot> method allows one
to create a frozen read-only copy of an entity (in constant time), useful when an entity must be queried from
a client without the risk of race conditions if another client is modifying the same entity concurrently.

\begin{figure}[ht]
\centering
\includegraphics[width=.9\linewidth]{figures/shared_entity}
\caption{Exemplification of a Takamaka shared entity and of its connections with the objects persisted in the blockchain.}
\label{figure.shared_entity}
\end{figure}
